TBD

### 2016-09-27 paper.tex
added more to geometry matrix text

\subsection{Redundant Array Geometry Mapping}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: We can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

Let $\phi_{ij}:\mathbb{N}^2\rightarrow\mathbb{N}^+$ be the mapping that maps composite antenna pairs to the unique redundant baseline indexes of an array. This mapping is not symmetric as 
$\phi_{ij} = 0$ if $i>j$. It is possible to construct a simple analytic expression for $\phi_{ij}$ when our array is in an east-west regular configuration:
\begin{equation}
\phi_{ij} = 
\begin{cases}
j-i&\textrm{if}~i<j\\
0&\textrm{otherwise}
\end{cases}.
\end{equation}
It becomes increasingly more difficult to construct analytic expressions of $\phi_{ij}$ for other more complicated array layouts.

We can also define the following symmetric variant of $\phi_{ij}$:
\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{ij}~\textrm{if}~i\leq j\\
\phi_{ji}~\textrm{if}~i>j
\end{cases}.
\end{equation}

@@

\subfigure[Hexagonal: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./HEX_phi.pdf}\label{fig:HEX_phi}}
\subfigure[Square: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./SQR_phi.pdf}\label{fig:SQR_phi}}
\subfigure[Regular east-west: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./REG_phi.pdf}\label{fig:REG_phi}}
\caption{In the top panel we have three different redundant antenna layouts. In the bottom panel we have the symmetric redundancy geometry mapping $\zeta_{ij}$
of each of the layouts in the top panel.}
\end{figure*}

If the mapping $\phi_{ij}$ is known and one is given one of the two antenna indexes that together form a redundant baseline as well as the redundant baseline index itself then it is possible 
to calculate the unknown antenna index. This can be calculated via the following two expressions:
\begin{equation}
\xi_{ij} = 
\begin{cases}
p~\textrm{if}~\exists! ~ p \in \mathbb{N} ~ s.t. ~(\phi_{pi} = j)\\
0~\textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
\psi_{ij} = 
\begin{cases}
q~\textrm{if}~\exists! ~ q \in \mathbb{N} ~ s.t. ~(\phi_{iq} = j)\\
0~\textrm{otherwise}
\end{cases}
\end{equation}

We use $\xi_{ij}$ to retrieve the first antenna index of the composite antenna pair associated with a particular baseline if the index of the first antenna in the composite antenna pair and the unique redundant baseline index are known, while we use $\psi_{ij}$ to obtain 
a similar result; the second antenna index of the composite antenna pair. \textbf{NB::} I still need to plot $\zeta_{ij}$ for different antenna layouts.

>>>>

\subsection{Redundant Array Geometry Function}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: We can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.

Let $\phi_{ij}:\mathbb{N}^2\rightarrow\mathbb{N}^+$ be the function that maps composite antenna pairs to the unique redundant baseline indexes of an array. We refer to this function 
as the redundant array geometry function in this paper. This mapping is not symmetric as 
$\phi_{ij} = 0$ if $i>j$. We can also define the following symmetric variant of $\phi_{ij}$:
\begin{equation}
\zeta_{ij} = 
\begin{cases}
\phi_{ij}~\textrm{if}~i\leq j\\
\phi_{ji}~\textrm{if}~i>j
\end{cases}.
\end{equation} 
It is possible to construct a simple analytic expression for $\zeta_{ij}$ when our array is in an east-west regular configuration: $\zeta_{ij} = |j-i|$. 
It becomes increasingly more difficult to construct analytic expressions of $\zeta_{ij}$ for other more complicated array layouts. The empirically constructed symmetric geometry
functions of three different redundant layouts are depicted in Fig.~\ref{fig:geometry_function}. We denote the range of $\zeta_{ij}$ with $\mathcal{R}(\zeta_{ij})$. The maximal element 
that $\zeta_{ij}$ can ascertain is denoted by $L$ and can be construed as the maximal number of unique redundant baselines which can be formed for a given 
array layout. Alternatively, we can interpret the symmetric geometry functions 
in Fig.~\ref{fig:geometry_function} as matrices. In this alternative paradigm, $\zeta_{ij}$ denotes a matrix entry instead. The dimension of these so called geometry 
matrices are $N\times N$, where $N$ denotes the number of antennas in the array.

@@

\subfigure[Hexagonal: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./HEX_phi.pdf}\label{fig:HEX_phi}}
\subfigure[Square: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./SQR_phi.pdf}\label{fig:SQR_phi}}
\subfigure[Regular east-west: $\zeta_{pq}$]
{\includegraphics[width=0.33\textwidth]{./REG_phi.pdf}\label{fig:REG_phi}}
\caption{In the top panel we have three different redundant antenna layouts, namely a hexagonal (left), square (middle) and a regular east-west (right) layout. 
In the bottom panel we have the respective symmetric redundancy geometry functions for the layouts on the top panel. We used 91 antennas
to construct the the hexagonal layout, while a 100 antennas where used in the square and east-west layouts. The maximal amount of redundant baselines that can be formed for 
the hexagonal, square and east-west layouts which are depicted in the top panel are 165, 180 and 99 respectively.\label{fig:geometry_function}}
\end{figure*}

If the mapping $\phi_{ij}$ is known and one is given one of the two antenna indexes that together form a redundant baseline as well as the redundant baseline index itself then it is possible 
to calculate the unknown antenna index. This can be calculated via the following two expressions:
\begin{equation}
\xi_{ij} = 
\begin{cases}
p~\textrm{if}~\exists! ~ p \in \mathbb{N} ~ s.t. ~(\phi_{pi} = j)\\
0~\textrm{otherwise}
\end{cases},
\end{equation}
and
\begin{equation}
\psi_{ij} = 
\begin{cases}
q~\textrm{if}~\exists! ~ q \in \mathbb{N} ~ s.t. ~(\phi_{iq} = j)\\
0~\textrm{otherwise}
\end{cases}
\end{equation}
We use $\xi_{ij}$ to retrieve the first antenna index of the composite antenna pair associated with a particular baseline, if the index of the first antenna in the composite antenna pair and the unique redundant baseline index are known, while we use $\psi_{ij}$ to obtain 
a similar result; the second antenna index of the composite antenna pair. \textbf{NB::} I still need to plot $\zeta_{ij}$ for different antenna layouts.
